% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage{CJKutf8}
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\hypersetup{breaklinks=true}
\hfuzz=20pt


% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
%%%%%%%%%%

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[L]{\textit{Jongpil Jeong}}
\fancyhead[R]{\textit{November 2025}}
\thispagestyle{empty} % Remove header from the first page

% Header
\begin{flushleft}
\href{https://scholar.google.com/citations?user=O-3pYeQAAAAJ&hl=en}{\textbf{\LARGE Jongpil Jeong}}\\[2pt] % Name
Master course \\ 
Department of Creative Informatics \\ 
Graduate School of Computer Science and Systems Engineering \\ 
Kyushu Institute of Technology \\ 
680--4, Kawazu, Iizuka, Fukuoka, Japan \\ 
\href{mailto:jeong.jongpil383@mail.kyutech.jp}{jeong.jongpil383@mail.kyutech.jp} \\%| \href{https://www.linkedin.com/in/JohnDoe}{www.linkedin.com/in/JohnDoe} | \href{https://JohnDoe/en/staff/single/59}{Organization page} \\ % Contact info \\
\href{tel:+82-10-8912-3304}{+82-10-8912-3304} [KR]
\\ \href{tel:+81-90-7269-3467}{+81-90-7269-3467} [JP]
\end{flushleft} 


\section*{EDUCATION}
\textbf{Kyushu Institute of Technology} \hfill Iizuka, Fukuoka, Japan\\
Master of Engineering, Graduate School of Computer Science and Systems Engineering \hfill \textit{Apr. 2024 — Mar. 2026(Expected)} \\
Department of Creative Informatics (Computer Science and Networks)  \hfill Cumulative GPA:\textbf{3.02/4.00} \\
Thesis (in progress): \textit{“Visibility restoration via spatial frequency domain interpretation under harsh conditions”} \\
Advisor: \href{https://scholar.google.com/citations?user=9sv1-5QAAAAJ&hl=en&oi=ao}{Prof. Min-Chul Lee} \\

\noindent
\textbf{Dong-A University} \hfill Busan, Korea \\
Bachelor of Engineering in Electronics Engineering \hfill \textit{Mar. 2018 — Feb. 2024} \\
(Top 10\%; 156 credits completed / 150 required) \hfill Cumulative GPA:\textbf{3.91/4.50} \\
Recipient of Academic Excellence Scholarships (5 semesters) \\

% Education Section
\section*{RESEARCH INTERESTS}

\begin{itemize}
    % \item Three-dimensional imaging system
    \item \textbf{Image Processing} / Computer Vision
    \item \textbf{Biomedical Imaging System}
    \item \textbf{Digital Holographic Microscopy (DHM)}
    % \item Computer vision
    \item Optical Signal Processing
    \item \textbf{Denoising / Deblurring Algorithm}
    % \item Data science
    \item Deep Learning / Machine Learning
\end{itemize} 

% \section*{SKILLS}
% \begin{tabularx}{\textwidth}{@{}lX@{}}
% \textbf{Languages}     & Korean (Native), English (\href{https://github.com/user-attachments/assets/f578b432-f7a8-410e-851c-852e9ae55378}{OPIc IH}), Japanese (Intermediate) \\ 
% \textbf{Programming}   & C/C++, Python, MATLAB \\
% \textbf{Libraries}     & PyTorch, TensorFlow, OpenCV, Qt, Pandas, NumPy, SciPy, Plotly \\
% \textbf{Tools / OS}    & Docker, \LaTeX, Digit Cam, Spinnaker SDK, Pylon SDK, Git, Linux, Windows, macOS \\ \\
% \end{tabularx}

% Projects Section
\section*{RESEARCH PROJECTS}
% KAKEN
\noindent 
\textbf{\begin{CJK}{UTF8}{min}煙等の散乱媒質による視界不良現場を可視化するための画像処理技術の研究\end{CJK}} \hfill Fukuoka, Japan\\ % Project name and location
Image processing techniques for visualizing poor-visibility scenes under scattering media \hfill Apr. 2024 | Present \\ 
\textit{Research Assistant} \hfill (Project: Apr. 2024--Mar. 2027) \\  % Project link and duration
Grant number: 24K01120 (Funded by KAKEN, JSPS) \\

% 소방청
\noindent 
\textbf{\begin{CJK}{UTF8}{min}視界が悪い災害現場を光信号処理とAIにより視界良好とするAR救援補助システムの開発\end{CJK}} \hfill Fukuoka, Tokyo, Japan\\% Project name and location
AR-based rescue assistance system using optical signal processing and AI for enhanced visibility \hfill May. 2024 | Mar. 2025 \\  in disaster environments \\
\textit{Research Assistant}  \\
Grant number: JPJ000255 (Funded by Fire and Disaster Management Agency of Japan) \\
Grant type: Consigned research \\ %(Funded by Fire and Disaster Management Agency of Japan)\\% Project link and duration

% KAKEN
\noindent
\textbf{\begin{CJK}{UTF8}{min}物体の360度3次元プロファイルを獲得可能なデジタルホログラフィック顕微鏡の開発\end{CJK}} \hfill Fukuoka, Japan\\ % Project name and location
Development of a 360-degree Digital Holographic Microscope (DHM) for 3D object profiling \hfill Apr. 2024 | Mar. 2025 \\
\textit{Research Assistant} \hfill (Participation period) \\  % Project link and duration 
Grant number: 23K19964 (Funded by KAKEN, JSPS) \\

% HITACHI
\noindent 
\textbf{\begin{CJK}{UTF8}{min}孵化前のニワトリにおける性別診断技術の開発\end{CJK}} \hfill Fukuoka, Gifu, Tokyo, Niigata, Ibaraki, Japan\\ % Project name and location
Development of pre-hatching sex determination technology for chickens \hfill Apr. 2024 | Nov. 2024 \\
\textit{Research Assistant} \hfill (Participation period) \\ % Project link and duration
Grant type: Joint Research (Funded by a private industry partner under NDA) \\

\newpage
% Paper publications
\section*{PUBLICATIONS}

% \noindent
\subsection*{Journal}
\begin{enumerate}[label={[\arabic*]}, start=1]
    % IEEE Access
    \item 
    \underbar{\textbf{J. Jeong}}, and M.-C. Lee,
    ``Scattering Medium Removal Using Adaptive Masks for Scatter in the Spatial Frequency Domain,''
    \textit{IEEE Access},
    vol. 13, pp. 72769--72777, 
    2025. \\
    DOI:\href{https://doi.org/10.1109/ACCESS.2025.3563369}{10.1109/ACCESS.2025.3563369} 
\end{enumerate} 

\subsection*{Conference}
\begin{enumerate}[label={[\arabic*]}, start=1]
    
    % 2025 ICCAS
    %--------------------------------------------------------------------------------------------------------------%
    \item 
    Y. Takahashi, \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``A research on scattering media removal and photon estimation using COLaNoPS,''
    \textit{Proc. ICCAS 2025}, (IEEE),
    % $25^{th}$ \textit{International Conference on Control, Automation and Systems}, 
    Incheon, Korea. 
    % pp. xxx-xxx, 
    % DOI: \href{https://doi.org/}{xxxxxxxxxxxxxxxxxxxxx},
    % (2025. 10) (Scopus).
    (Accepted)

    % 2025 ICMV
    %--------------------------------------------------------------------------------------------------------------%
    \item 
    \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``Advanced scattering media removal by modified ARMS and restoration of color information,'' 
    \textit{Proc. ICMV 2025}, (SPIE),
    % $18^{th}$ \textit{International Conference on Machine Vision}, 
    Paris, France. 
    % pp. xxx-xxx, 
    % DOI: \href{https://doi.org/}{xxxxxxxxxxxxxxxxxxxxx},
    % (2025. 10) (Scopus).
    (Accepted).  

    \item 
    S. Song, \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``Single Haze Removal Method using Peplography,'' 
    \textit{Proc. ICMV 2025}, (SPIE),
    % $18^{th}$ \textit{International Conference on Machine Vision}, 
    Paris, France. 
    % pp. xxx-xxx, 
    % DOI: \href{https://doi.org/}{xxxxxxxxxxxxxxxxxxxxx},
    % (2025. 10) (Scopus).
    (Accepted).

    % 2025 ITC-CSCC
    %--------------------------------------------------------------------------------------------------------------%
    \item 
    \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``Scattering media removal under the harsh conditions using adaptive removal via mask for scatter,'' 
    % $40^{th}$ \textit{International Technical Conference on Circuits/Systems, Computers and Communications}, 
    \textit{Proc. ITC-CSCC 2025}, (IEEE),
    Seoul, Korea. \\
    % pp. xxx-xxx, \\
    DOI:\href{https://doi.org/10.1109/ITC-CSCC66376.2025.11137793}{10.1109/ITC-CSCC66376.2025.11137793}
    % Jul. 2025. (Scopus).
    % (Proceeding).
    
    \item 
    K. Nakamura, \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``Adaptive Optimization of Kalman Filtering in Digital Holographic Microscopy for Improved Noise Reduction,'' 
    % $40^{th}$ \textit{International Technical Conference on Circuits/Systems, Computers and Communications}, 
    \textit{Proc. ITC-CSCC 2025}, (IEEE),
    Seoul, Korea. \\
    % pp. 1--6, \\
    DOI:\href{https://doi.org/10.1109/ITC-CSCC66376.2025.11137616}{10.1109/ITC-CSCC66376.2025.11137616}
    % Jul. 2025. (Scopus).
    % (Proceeding).
    
    \item 
    S. Kim, \underbar{\textbf{J. Jeong}}, M. Cho, and M.--C. Lee, 
    ``Advanced double random phase encryption for simultaneous two primary data,'' 
    % $40^{th}$ \textit{International Technical Conference on Circuits/Systems, Computers and Communications}, 
    \textit{Proc. ITC-CSCC 2025}, (IEEE),
    Seoul, Korea. \\
    % pp. 1--5, \\
    DOI:\href{https://doi.org/10.1109/ITC-CSCC66376.2025.11137702}{10.1109/ITC-CSCC66376.2025.11137702}
    % Jul. 2025. (Scopus).
    % (Proceeding).
    
    % 2024 ICCAS
    %--------------------------------------------------------------------------------------------------------------%
    \item 
    T. Ono, \underbar{\textbf{J. Jeong}}, H.--W. Kim, M. Cho, and M.--C. Lee, 
    ``Kalman filtering optimization in digital holographic microscopy (DHM),'' 
    % $24^{th}$ \textit{International Conference on Control, Automation and Systems}, 
    \textit{Proc. ICCAS 2024}, (IEEE),
    Jeju, Korea.\\
    % pp. 786--791, \\
    DOI:\href{https://doi.org/10.23919/ICCAS63016.2024.10773243}{10.23919/ICCAS63016.2024.10773243} 
    % Oct. 2024. 
    
    % 2024 JCSSE
    %--------------------------------------------------------------------------------------------------------------%
    \item 
    \underbar{\textbf{J. Jeong}}, H.--W. Kim, M. Cho, and M.--C. Lee, 
    ``A study of noise reduction algorithm using statistical optimization in digital holographic microscopy,'' 
    \textit{Proc. JCSSE 2024}, (IEEE),
    % $21^{st}$ \textit{International Joint Conference on Computer Science and Software Engineering}, 
    Phuket, Thailand.\\
    % pp. 68--73, \\
    DOI:\href{https://doi.org/10.1109/JCSSE61278.2024.10613728}{10.1109/JCSSE61278.2024.10613728} 
    % Jun. 2024. 
    
    
\end{enumerate} 

% \noindent
\subsection*{Patents}
\subsubsection*{International Patents (PCT)}
\begin{enumerate}[label={[\arabic*]}, start=1]
    \item 
    M.--C. Lee and \underbar{\textbf{J. Jeong}},
    \begin{CJK}{UTF8}{min}``画像処理装置、画像処理方法および画像処理プログラム,''\end{CJK} \hfill {Pending}\\
    ``Image processing apparatus, image processing method, and image processing program,'' \hfill {PCT/S2025--0068-N0}\\
    PCT Patent.
\end{enumerate}

\noindent
% \subsubsection*{Domestic Patents \hfill Japan}
\subsubsection*{Domestic Patents (JST) \hfill \normalfont{Japan}} 
\normalfont{
    \begin{enumerate}[label={[\arabic*]}, start=1]
        \item 
        M. Kamide, O. Shiba, K. Ozawa, T. Nakaya, T. Tagami, M.--C. Lee and \underbar{\textbf{J. Jeong}},           \hfill {Sep. 18, 2025} \\
        \begin{CJK}{UTF8}{min}``雌雄判定システム及び雌雄判定方法,''\end{CJK}                                              \hfill {\begin{CJK}{UTF8}{min}特願\end{CJK} 2025--154965}\\                 
        ``Sex identification service provision system and sex identification service provision method,'' \\
        Japanese Patent. 
        % (Not publicly accessible at this time due to confidentiality under Japanese patent law.)
        \item 
        M.--C. Lee and \underbar{\textbf{J. Jeong}},
        \begin{CJK}{UTF8}{min}``画像処理装置、画像処理方法および画像処理プログラム,''\end{CJK}                              \hfill {Jun. 10, 2025} \\
        ``Image processing apparatus, image processing method, and image processing program,''                    \hfill {\begin{CJK}{UTF8}{min}特願\end{CJK} 2025--097331} \\
        Japanese Patent. 
        % (Not publicly accessible at this time due to confidentiality under Japanese patent law.)
        \item 
        M.--C. Lee and \underbar{\textbf{J. Jeong}},
        \begin{CJK}{UTF8}{min}``画像処理装置、画像処理方法および画像処理プログラム,''\end{CJK}                              \hfill {Dec. 09, 2024} \\
        ``Image processing apparatus, image processing method, and image processing program'' \hfill {\begin{CJK}{UTF8}{min}特願\end{CJK} 2024--214715}\\
        Japanese Patent.
        
        \item[*] In accordance with Japanese patent law, these applications are kept confidential and are not publicly disclosed for 18 months following their filing. 
    
    \end{enumerate} 
}

\newpage% Experience Section
\section*{Additional Research Experience}

\noindent
\textbf{\href{https://3cholab.wordpress.com/정보/}{Computational, Holographic and Optical signal processing Lab.}} \hfill Anseong, Gyunggi-do, Korea\\ % Company name and location
\textbf{at Hankyung National University} \hfill Jan. 2024 | Feb. 2024 \\
\textit{Visiting Research Student} % Position and duration
\begin{itemize}
    \item Integral Imaging Systems
    \item Principle of image encryption such as double random phase encryption (DRPE) \\
\end{itemize}

\noindent
\textbf{\href{https://leelab.csn.kyutech.ac.jp}{3D Optical Imaging System Lab.} at Kyushu Institute of Technology} \hfill Fukuoka, Japan\\ 
\textit{Short-Term Visiting Researcher} (Winter 2022 \& Summer 2023) \hfill Jan. |  Feb. \& Jul.  | Aug. 2023\\
Advisor: Prof. Min-Chul Lee
\begin{itemize}
    \item Studied Digital Dolographic Microscopy(DHM) and phase error correction  
    \item Developed noise reduction algorithms under low-light (photon-starved) conditions
    \item Restored low-light images using photon-counting techniques 
    \item Visibility enhancement under harsh conditions through the scattering media \\
\end{itemize}

\noindent
\textbf{\href{https://soc.donga.ac.kr/soc/Main.do}{SoC Design Lab.} at Dong-A University} \hfill Busan, Korea\\ % Company name and location
\textit{Undergraduate Research Intern} \hfill Sep. 2022 | Jul. 2023 \\
Advisor: Prof. Bongsoon Kang \\
Completed the \href{https://github.com/user-attachments/assets/583762df-f208-4216-b836-a6a1921ec34b}{IDEC SoC Design Course} (48 hours, Spring 2023), which initiated my interest in image processing and computational systems. \\
Topics covered: Verilog HDL fundamentals, structural and dataflow modeling, and algorithmic-level design.
\begin{itemize}
    \item Basic image processing techniques.
    \item Principle of machine learning.
    \item Programming with C/C++, MATLAB, Python, and Verilog \\
\end{itemize}





\section*{Relevant Coursework}
% KOCW
\paragraph{\large{\href{https://www.kocw.net/home/index.do}{Korea OpenCourseWare (KOCW)}}} \hfill Online, Korea
\begin{itemize}
    \item \href{https://github.com/user-attachments/assets/d8024d63-359a-493b-9cb2-774e36a03f62}{Digital Image Processing}                                              \hfill 2025
\end{itemize}

% IDEC
\paragraph{\large{\href{https://www.idec.or.kr/main/}{IC Design Education Center (IDEC)}}}  \hfill Online, Korea
\begin{itemize}
    %2024
    \item \href{https://github.com/user-attachments/assets/234ad610-a051-4140-9f20-48ca4d8e4d42}{Implementation of CNN's FPGA with Verilog HDL}                         \hfill 2024
    \item \href{https://github.com/user-attachments/assets/68b0ae05-462b-4750-93ba-1bc4072dab66}{Design embedded systems based on FPGA}
    \item \href{https://github.com/user-attachments/assets/8fbda935-4b41-44f7-b83a-8d284f003168}{Data structure and algorithm}                                          
    \item \href{https://github.com/user-attachments/assets/805bbc13-3e6e-43d6-af75-df31f728d607}{FreeRTOS porting and utilization through Cortex-M processor}           
    \item \href{https://github.com/user-attachments/assets/707a4f8e-3b5a-4246-a763-81e2729f9cb2}{MIMO - theory and improvement}                                         
\end{itemize}

\begin{itemize}
    %2023
    % \vspace{0.5em}
    \item \href{https://github.com/user-attachments/assets/2d45999d-1f66-467c-b956-e16b5ed71593}{Stereovision for autonomous driving system}                            \hfill 2023
    \item \href{https://github.com/user-attachments/assets/32bfc1d6-18cf-44a4-83dc-209b4f4686ac}{Design digital system utilized Verilog}
    \item \href{https://github.com/user-attachments/assets/094a58df-f320-45fb-aba3-707f4a7fd8f7}{Neural network hardware accelerator ``Architecture''}
    \item \href{https://github.com/user-attachments/assets/9f74252d-eae5-40b2-b305-ea90576100aa}{DSP with MATLAB}
    \item \href{https://github.com/user-attachments/assets/0fc8c167-bef1-4857-a664-a1b82c95e306}{Foundation of CUDA-based GPU Programming}    
\end{itemize}
\begin{itemize}
    % \vspace{0.5em}             
    % 2022             
    \item \href{https://github.com/user-attachments/assets/b4e013f1-d7b8-4505-a4f5-12e270097549}{PLL Design and Jitter Interpretation}                                  \hfill 2022
    \item \href{https://github.com/user-attachments/assets/73933790-2b15-46ae-8ac2-c6eaf31d9e01}{Foundation of reinforcement learning}                                  
\end{itemize}


% KAIST
\paragraph{\large{\href{https://gsds.kaist.ac.kr}{Korea Advanced Institute of Science and Technology (KAIST)}}}  \hfill Online, Korea
\begin{itemize}
    % \item \href{https://github.com/user-attachments/files/21983055/IMG_20250826_0002_NEW_0001.pdf}{AI in Biomedical Imaging - AI in Healthcare Technique}               \hfill 2025
    \item \href{https://github.com/user-attachments/assets/b404e1df-2798-48de-8385-c9a6c7389b38}{Microdegree from Graduate School of Data Science}                      \hfill 2023
\end{itemize}

\newpage
\section*{Awards, Scholarships and Tuition Waivers}
\large{\textbf{\href{https://github.com/user-attachments/assets/53461ed5-0c97-4db9-8181-8551847832b3}{Best Poster Presentation Award}}} (IMCV 2025) \hfill Paris, France \\ \\
\noindent
% Company name and location
\large{\textbf{Kyushu Institute of Technology}} \hfill Fukuoka, Japan
% \subsection*{Kyushu Institute of Technology} \hfill Fukuoka, Japan\\
% \subsubsection*{Waivers from Tuition Fees}
\begin{itemize}
    \item \textbf{Waivers from Tuition Fees}
    \begin{itemize}
        \item 2025, $1^{st}$ semester 
        \item 2024, $1^{st} / 2^{nd}$ semester 
    \end{itemize} 
\end{itemize}
% \textbf{Waivers from Tuition Fees}
% \begin{itemize}
%     \item 2025, $1^{st}$ semester 
%     \item 2024, $1^{st} / 2^{nd}$ semester 
% \end{itemize} 
% \noindent \\
% \subsection*{Dong-A University} 
\large{\textbf{Dong-A University}} \hfill Busan, Korea
% \subsubsection*{Academic Excellence Scholarship}
\begin{itemize}
    \item \textbf{Academic Excellence Scholarship}
    \begin{itemize}
        \item 2023, $1^{st} / 2^{nd}$ semester 
        \item 2022, $1^{st}$ semester 
        \item 2021, $2^{nd}$ semester 
        \item 2018, $2^{nd}$ semester 
    \end{itemize} 
    % \subsubsection*{Advisory Professor Scholarship from Dong-A University}
    \item \textbf{Advisory Professor Scholarship from Dong-A University}
    \begin{itemize}
        \item 2022, $2^{nd}$ semester 
    \end{itemize} 
    % \subsubsection*{Undergraduate Education Assistant Scholarship from Dong-A University}
    \item \textbf{Undergraduate Education Assistant Scholarship from Dong-A University}
    \begin{itemize}
        \item 2023, $1^{st}/2^{nd}$ semester 
        \item 2022, $2^{nd}$ semester 
    \end{itemize} 
\end{itemize}





\section*{Leadership \& Volunteering}
\noindent
\large{\textbf{\href{https://innovationjapan.jst.go.jp}{\begin{CJK}{UTF8}{min}大学見本市2025 -- イノベーション・ジャパン\end{CJK}}}}  \hfill Tokyo, Japan\\ % Company name and location
Innovation Japan 2025  \hfill Aug. 21 2025 | Aug. 22 2025  \\% Position and duration
\textit{Student Staff} \\

\noindent
\large{\textbf{\href{https://www.iizuka.kyutech.ac.jp/admissions/open/open2025}{\begin{CJK}{UTF8}{min}オープンキャンパス 2025\end{CJK}}}}  \hfill Fukuoka, Japan\\ % Company name and location
Open Campus 2025 (Iizuka Campus, Kyushu Institute of Technology) \hfill Jul. 19 2025 | Jul. 20 2025 \\
\textit{Student Staff} \\ % Position and duration

\noindent
\large{\textbf{\begin{CJK}{UTF8}{min}{協定校との国際交流及びセミナー}\end{CJK}}} \hfill Fukuoka, Japan\\
International Capstone Design Presentation with Partner Universities  \hfill Jan. 2025 \\
\textit{Participant (Student Delegate)} \\

\noindent
\large{\textbf{\begin{CJK}{UTF8}{min}{協定校との国際共同研究打合せ及び共同セミナー}\end{CJK}}} \hfill Kumamoto, Japan \\
International Joint Research Meeting and Seminar \hfill Aug. 9 2024 | Aug. 10 2024 \\
\textit{Participant (Student Delegate)} \\

% \noindent
% \textbf{Hands}  \hfill Busan, Korea\\ % Company name and location
% Member \hfill Mar. 2021 | Feb. 2024 \\% Position and duration

\noindent
\large{\textbf{Embedded Systems Lab.}}  \hfill Busan, Korea\\ % Company name and location
\textit{Leader} \hfill Sep. 2023 | Dec. 2023% Position and duration
\begin{itemize}
    \item Embedded system design using ATMega128A
    \item Embedded system control using the I/O ports and potentiometer 
\end{itemize} 

\noindent
\large{\textbf{Donga Challenge}}  \hfill Busan, Korea\\ % Company name and location
\textit{Leader} \hfill Sep. 2023 | Dec. 2023% Position and duration
\begin{itemize}
    \item Self-directed learning and project-based teamwork initiative
    \item Teaching basic programming (Python) and data analysis using Pandas and NumPy
\end{itemize} 

\noindent
\large{\textbf{Digital System Lab.}}  \hfill Busan, Korea\\ % Company name and location
\textit{Leader} \hfill Sep. 2023 | Dec. 2023% Position and duration
\begin{itemize}
    \item Basic programming (C/C++) and embedded system desing using ATMega128A
    \item Teaching digital logic design and Verilog HDL
\end{itemize} 

\noindent
\large{\textbf{Dong-A Ping-Pong Association (DAPPA)}}  \hfill Busan, Korea\\ % Company name and location
\textit{President} \hfill Mar. 2021 | Feb. 2022 \\% Position and duration

% \section*{Military Service}
% \noindent
% \textbf{\large{Republic of Korea Army}} \hfill Haman-gun, Gyeongsangnam-do, Korea \\
% \textit{Sergeant (E-5), Active Duty Soldier} \hfill Apr. 2019 | Nov. 2020
% \begin{itemize}
%     % \item \href{https://github.com/user-attachments/files/21983055/IMG_20250826_0002_NEW_0001.pdf}{AI in Biomedical Imaging - AI in Healthcare Technique}               \hfill 2025
%     \item \href{https://github.com/user-attachments/assets/584d8f84-5bbe-4a71-9ae3-bda5ce40bd6f}{Award for Outstanding Army Warrior}  
%     \item \href{https://github.com/user-attachments/assets/d3b82b44-dff0-4d58-a944-747f46f8a50e}{Certificate of Appointment as Squad Leader}
%     \item \href{https://github.com/user-attachments/assets/8565647d-3609-4866-8e18-fbdf9a9e227c}{Appointment Certificate as Squad Representative Soldier}
%     \item \href{https://github.com/user-attachments/assets/f4f76912-92a7-440e-b8a2-4ce52b1ec39a}{Commendation for Exemplary Soldier}
% \end{itemize}
% \begin{itemize}
%     \item \textbf{\href{https://viewscreen.githubusercontent.com/view/pdf?browser=safari&bypass_fastly=true&color_mode=auto&commit=2215c6ebbad5842a11bd9c9dcda1810569893183&device=unknown_device&docs_host=https%3A%2F%2Fdocs.github.com&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4a6f6e6770696c303931312f4a6f6e6770696c303931312e6769746875622e696f2f323231356336656262616435383432613131626439633964636461313831303536393839333138332f6173736574732f494d475f32303235303832365f303030335f4e45572e706466&link_underline_enabled=true&logged_in=true&nwo=Jongpil0911%2FJongpil0911.github.io&path=assets%2FIMG_20250826_0003_NEW.pdf&platform=mac&repository_id=767055468&repository_type=Repository&version=18#9a5379c5-c432-422f-861c-179ec99d82ff}{Award for Outstanding Army Warrior}} \hfill 2020
% \end{itemize}




% Completed mandatory military service as a squad leader in an artillery unit; responsible for team coordination, safety checks, and equipment management.
% \begin{itemize}
%     \item \# Description of your job duty and responsibilities.
%     \item \# Description of your job duty and responsibilities.
%     \item \# Description of your job duty and responsibilities.
%     \item \# Description of your job duty and responsibilities.
% \end{itemize}


% \section*{ENGLISH \& GRE TESTS}
%     \begin{tabularx}{1\textwidth}{
%     >{\raggedright\arraybackslash}X 
%    >{\raggedright\arraybackslash}X }
%       \textbf{IELTS (Academic): 7.5} (overall score)&   \textbf{GRE General Test:}\\ \\
%     Listening: XX | Reading: XX & Quant: XXX | Verbal: XXX\\
%     Speaking: XX   | Writing: XX& Analytical writing: X\\
%     Test date: \#Month \#Year &Test date: \#Month \#Year
%     \end{tabularx}

% Skills Section


% \section*{REFERENCES}
% \textbf{Prof. Min-Chul Lee}\\
% \textit{Associate professor, Department of Computer Science and Networks, Graduate School of Computer Science and Systems Engineering, Kyushu Institute of Technology, Iizuka, Fukuoka, Japan}\\
% E-mail: \href{mailto:lee@csn.kyutech.ac.jp}{lee@csn.kyutech.ac.jp}\\
% Scholar Profiles: \href{https://leelab.csn.kyutech.ac.jp}{Lee Lab.} | \href{https://scholar.google.com/citations?user=9sv1-5QAAAAJ&hl=en&oi=ao}{Google Scholar}\\ \\
% \textbf{Prof. Myungjin Cho}\\
% \textit{Professor, School of ICT, Robotics and Mechanical Engineering, IITC, Hankyong National University, Anseong, Kyonggi-do, Korea}\\
% E-mail: \href{mailto:mjcho@hknu.ac.kr}{mjcho@hknu.ac.kr}\\
% Scholar Profiles: \href{https://3cholab.wordpress.com}{3CHO Lab.} | \href{https://scholar.google.com/citations?hl=en&user=WAvCU2kAAAAJ}{Google Scholar}\\ \\
% \textbf{Prof. Bongsoon Kang}\\
% \textit{Professor, Department of Eletronics Engineering, Collage of Engineering, Dong-A University, Busan, Korea}\\
% E-mail: \href{mailto:bongsoon@dau.ac.kr}{bongsoon@dau.ac.krn}\\
% Scholar Profiles: \href{https://soc.donga.ac.kr/soc/Main.do}{SoC Design Lab.} | \href{https://www.dbpia.co.kr/author/authorDetail?ancId=810834}{DBpia}\\ \\
% End document
\end{document}
